---
title: "Iris Dynamic Regression"
author: "rucrbser"
date: "May 8, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Presentation Description

* This presentation is about the **Dynamic Linear Regression** from the iris dataset.

* We bulid a Shiny Applicaiton to dynamically observe the linear regression.

* There are two tabs in this application to show different interactive relationships between different variables.

* We can randomly sample from this dataset different samples to observe variation of the linear regression.

* And surely for fun, there selectively displays the scatter smoothing linear regression model.


## Dynamic Linear Regression between Petal

```{r}
newiris <- iris[sample(dim(iris)[1], 75), ]
fit <- lm(Petal.Width ~ Petal.Length, data = newiris)
with(newiris, plot(Petal.Length, Petal.Width, pch = 20, main = "Randomly sample 75 observations"))
abline(fit, col = "red", lwd = 4)
```


## Dynamic Linear Regression between Sepal

```{r}
newiris <- iris[sample(dim(iris)[1], 75), ]
fit <- lm(Sepal.Width ~ Sepal.Length, data = newiris)
with(newiris, plot(Sepal.Length, Sepal.Width, pch = 20, main = "Randomly sample 75 observations"))
abline(fit, col = "red", lwd = 4)
```


## The Shiny Application

We can interact with our visualizations to dynamically observe the Linear Regression variation from 
the Shiny Application [Iris Dynamic Regression](https://rucrbser.shinyapps.io/Iris_Dynamic_Regression/).






